---
title: "Tidy and join tables"
format: html
---

# Instructions

This week you learned about tidying and joining data sets with the tidyr (pronounced tidy-R) and dplyr packages.

Joining data sets can be deceptively tricky. It is important to keep in mind that prepping and inspecting the tables you're working with *before* you do a join is often more important (and takes more time) than doing the join itself.

You'll use some of these skills in the milestone to the right.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/auto-insurance/assets/auto-insurance_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false

# Load your packages here

```

## Tidy and join

In this milestone, you'll join two data sets to examine both the number of claims and the amount claimed under different insurance policies. To do this, you'll need to use the data in `claims.csv` alongside the data you've been using in `policies.csv`. Both data sets are stored in your `data/` directory.

## Recreation

### Part 1 - Import

Before you begin, you will need to import your data sets. Use the code chunk below to read two data sets from the `data/` directory:

1. `policies.csv`, save it as `policies`
2. `claims.csv`, save it as `claims`

```{r}
#| label: recreation-import

```

### Part 2 - Summarize claims

Notice that in the `claims` data set, many policies have multiple associated claims. Before you join the policies and claims data together, you'll need to first summarize the `claims` data set such that there is one row per policy ID.

Your task is to transform `claims`. You will need to:

1. Group the data by `policy_id`
2. Compute the following summary statistics:
    - `claim_count`: the total number of claims
    - `total_claim_amount`: the sum of the claim amounts

Work in the code chunk below. Save the result as `claims_summarized`. We will use it in the next section.

```{r}
#| label: recreation-summarize

```

### Part 3 - Join tables and summarize

Now that you have summarized the claims data, let's join it with the policies data. First, run the code below to recreate `policies_recode` from the previous milestone:

```{r}
#| label: recode
policies_recode <-
  policies |>
  mutate(
    driver_age_group = case_when(
      driver_age < 25 ~ "Under 25",
      driver_age >= 25 & driver_age < 50 ~ "25-49",
      driver_age >= 50 & driver_age < 75 ~ "50-74",
      driver_age >= 75 ~ "75 and above"
    ),
    .after = driver_age
  )
```

Run the code below to see a table.

```{r}
#| label: recreate-this
#| message: false
solution <- readr::read_csv("data/milestone04.csv")
solution
```

Your task is to use what you've learned about the dplyr package to transform `policies_recode` and `claims_summarized` into this table. You will need to do some pre-join checks:

1. Which variables can you join on?
2. Do the data sets have any mismatched observations?
3. Perform any necessary data cleaning.
4. Check again as needed!

Then:

1. Join the `policies_recode` and `claims_summarized` data sets
2. Group the joined data by `driver_age_group`
3. Compute two useful summary measures:
    - `claim_amount_mean`, mean dollar amount of claims (based on `total_claim_amount`)
    - `n`, number of observations in each group

Work in the code chunk below. Save the result as `policies_claims_age`.

```{r}
#| label: recreation-join

```

Run the following code chunk to test whether you have the same answer as the solution:

```{r}
#| label: compare
#| eval: false
waldo::compare(policies_claims_age, solution, tolerance = 1e-4, ignore_attr = c("class", "groups"))
```

## Extension

Using the code chunk below, investigate a single research question about this data, using the skills you have learned this week and in previous weeks of Academy. Some ideas:

1. Create a visualization using the joined data from the milestone recreation. Use this visualization as the starting point for your own further investigation of the data. Use at least one data transformation step and one graph to start addressing your questions.
2. Consider inspecting the data quality of your joined table -- e.g. for how many policies with at least one recorded claim in `policies_recode` are there no matches in `claims_summarized`? (Hint: Inspect NAs in the newly appended columns of your joined table, or consider a filtering join.)
3. For how many policies in the joined table is there disagreement between your two source data sets (`policies_recode` and `claims_summarized`) about _how many claims were made_ under the policy?
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. Complete a data wrangling task relevant to your data (tidying and/or reshaping/pivoting your data); if appropriate, join your data with a second data set (filtering or mutating join)
3. Show summary tables of your data throughout these transformations


```{r}
#| label: extension

```
