---
title: "Work with data types"
format: html
---

# Instructions

This week, you worked with three new data types in R -- factors, strings, and date-times -- using the forcats, stringr, and lubridate packages, respectively.

In this milestone, you will practice reordering factor levels to create more polished visualizations of the data.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/auto-insurance/assets/auto-insurance_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false
```

## Data types

In this milestone, you'll visualize the differences in average claim size by age group and area code, using factor reordering to meaningfully sort the age group variable.

## Recreation

### Part 1 - Import

Before you begin, you will need to import your data sets. Use the code chunk below to read two data sets from the `data/` directory:

1. `policies.csv`, save it as `policies`
2. `claims.csv`, save it as `claims`

```{r}
#| label: recreation-import

```

### Part 2 - Join and summarize

Run the code chunk below to recreate `claims_summarized` and `policies_recode` from previous milestones, then join them together into `policies_full`.

```{r}
#| label: prep-data
# summarize claims data
claims_summarized <-
  claims |>
  group_by(policy_id) |>
  summarize(
    claim_count = n(),
    total_claim_amount = sum(claim_amount, na.rm = TRUE)
  ) |>
  ungroup()

# recode age
policies_recode <-
  policies |>
  mutate(
    driver_age_group = case_when(
      driver_age < 25 ~ "Under 25",
      driver_age >= 25 & driver_age < 50 ~ "25-49",
      driver_age >= 50 & driver_age < 75 ~ "50-74",
      driver_age >= 75 ~ "75 and above"
    ),
    .after = driver_age
  )

# join data
policies_full <-
  policies_recode |>
  left_join(claims_summarized, by = "policy_id")
```

Next, run the code below to see a table. This table summarizes the average claim amount for each combination of driver age group and area code.

```{r}
#| label: recreate-this-1
#| message: false
solution <- readr::read_csv("data/milestone05.csv")
solution
```

Your task is to use `policies_full` to create this table. You will need to:

1. Group the data by `driver_age_group` and `area`
2. Compute two summary measures:
    - `claim_amount_mean`, mean of `total_claim_amount`
    - `n`, number of observations in each group

Work in the code chunk below. Save your result as `plot_data`; we will use it in Part 3.

```{r}
#| label: recreation-summarize

```

Run the following code chunk to test whether you have the same answer as the solution:

```{r}
#| label: compare
#| eval: false
waldo::compare(plot_data, solution, tolerance = 1e-4, ignore_attr = c("class", "groups"))
```

### Part 3 - Reorder factor levels

If you make a bar plot of `plot_data`, the order of driver age groups on the x axis is arbitrary (alphabetical). Let's give the age groups a more principled order before we publish this plot.

Using the File Explorer, navigate to the `images/` directory, then click on `milestone05.png` to open an image.

You should see a plot in which the driver age groups are ordered by increasing age. Your task is to recreate this plot.

Use the chunk below to recreate this plot. (*Hint*: Use a forcats function to turn the `driver_age_group` variable into a factor with a set order, then map `area` to the `fill` aesthetic and use `position = "dodge"` in your geom.)

```{r}
#| label: recreation-visualize

```

## Extension

Using the code chunk below, investigate a research question about this data, using the skills you have learned this week and in previous weeks of Academy. Some ideas:

1. How do average insurance claim amounts (or counts) vary by vehicle brand? Create a plot to visualize this, utilizing factor reordering and/or string manipulation to create a meaningful order of vehicle brands in your plot.
2. Which regions show the highest and lowest average claim amounts (or number of claims)? Create a plot to visualize this, ordering the data in your plot by descending order of average claim amount (or count).
3. The plot you made in your recreation shows a strong pattern in the "Under 25" age group -- which data point(s) are driving this pattern? Does the plot look different if you first remove outliers?
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. If your data contains ...
  ... date-time data, use a lubridate function to correctly format your date-time variables
  ... string data, use a stringr function to manipulate your string variables
  ... categorical data, use a forcats function to modify the factor levels of your categorical variables (reorder, recode, etc.)
3. Using a table or graph, present a meaningful subset of your modified data

```{r}
#| label: extension

```
