---
title: "Summarize data"
format: html
---

# Instructions

This week, you learned several new functions from dplyr (pronounced DEE-ply-er), a commonly-used package from the tidyverse for wrangling data. You also learned some new ways to enhance your plots.

You'll use these skills to compute summary information for each vehicle brand.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/auto-insurance/assets/auto-insurance_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false

# Load your packages here

```

## Summarize data

In this milestone you'll group the data by vehicle brand and then summarize the results to calculate the number of policies and claims for each brand.

## Recreation

### Part 1 - Import

Before you begin, you will need to import your data set. Use the code chunk below to read the data from the data file `policies.csv`, which is stored in the `data/` folder in your working directory. Be sure to save the data to an object named `policies`.

```{r}
#| label: recreation-import

```

### Part 2 - Summarize data

Run the code below to see a table.

```{r}
#| label: recreate-this
#| message: false
solution <- readr::read_csv("data/milestone02.csv")
solution
```

Your task is to use what you've learned about the dplyr package to transform `policies` into this table. You will need to:

1. Group the data by vehicle brand
2. Summarize `total_policies`, `total_claims` and `mean_claims` for each group

Work in the code chunk below. Save the result as `brand_summary`.

```{r}
#| label: recreation-summary

```

Run the following code chunk to test whether you have the same answer as the solution:

```{r}
#| label: compare
#| eval: false
waldo::compare(brand_summary, solution, tolerance = 1e-4)
```

## Extension

Using the code chunk below, investigate a single research question about this data, using the data wrangling skills you learned this week. Some ideas:

1. Data visualization is often an easier way to see patterns than numbers in a table. Build a graph from your summary table of vehicle brands. Do you see any relationship between vehicle brand and the number of policies or claims?
2. Do the number of policies or claims vary by area code or region?
3. Do you see any patterns in the number of policies or claims when grouping the data by _both_ vehicle brand and area code (or region)?
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. Use `group_by()` and `summarize()` to produce simple a table from some subset of your data
3. Create a related graph of this data subset using ggplot


```{r}
#| label: extension

```
