---
title: "Wrangle rows and columns"
format: html
---

# Instructions

This week, you learned several more functions from the dplyr package (pronounced DEE-ply-er). These functions help you work with the rows and columns in your data set.

You'll use these skills to recode age as a categorical variable and investigate patterns across age groups.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/auto-insurance/assets/auto-insurance_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false

# Load your packages here

```

## Create and select columns

In this milestone you will create a new variable in `policies` that assigns each policy holder to an age group. Then, you'll summarize the data to find the average number of claims per policy in each group.

## Recreation

### Part 1 - Import

Before you begin, you will need to import your data set. Use the code chunk below to read the data from the data file `policies.csv`, which is stored in the `data/` folder in your working directory. Be sure to save the data to an object named `policies`.

```{r}
#| label: recreation-import

```

### Part 2 - Recode

We would like to first create age group categories.

Your task is to use what you've learned about the dplyr package to transform `policies`. You will need to:

1. Using the `driver_age` column, create a new column called `driver_age_group` that assigns each policy holder to one of the following age groups:

   - "Under 25"
   - "25-49"
   - "50-74"
   - "75 and above"

2. Place the `driver_age_group` column immediately _after_ the `driver_age` column. (*Hint*: Is there an argument you can use within `mutate()`?)

Work in the code chunk below. Save your resulting table as `policies_recode`; we will use it in Part 3.

```{r}
#| label: recreation-recode

```

### Part 3 - Summarize

Now that you have age represented as a categorical variable, you can summarize the data to find the average number of claims per policy in each age group. Run the code below to see a table.

```{r}
#| label: recreate-this
#| message: false
solution <- readr::read_csv("data/milestone03.csv")
solution
```

Your task is to use what you've learned about the dplyr package to transform `policies_recode` into this table. You will need to:

1. Group the data by `driver_age_group`
2. Calculate the mean number of claims (`num_claims`) for each group, saving the result as `mean_claims`
3. Arrange the rows in descending order of the mean number of claims

Work in the code chunk below. Save your resulting table as `policies_age`.

```{r}
#| label: recreation-summarize

```

Run the following code chunk to test whether you have the same answer as the solution:

```{r}
#| label: compare
#| eval: false
waldo::compare(policies_age, solution, tolerance = 1e-4, ignore_attr = c("class", "groups"))
```

## Extension

Using the code chunk below, investigate a single research question about this data, using the additional data wrangling skills you learned this week. Some ideas:

1. Recode `vehicle_age` into meaningful categories. What patterns do you see based on these categories?
2. The number of insurance claims seems to be a highly skewed distribution. Try some different approaches to recoding to group or bin this variable in a meaningful way.
3. Recode `bonus_malus` into a categorical variable, and then investigate patterns in the data based on this new variable. (Refer to the data dictionary for more details.)
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. Create at least one new variable in your data set (using `mutate()` and/or `summarize()`), or use other dplyr functions to alter your data
3. Use your updated data set to create at least one graph and/or table

```{r}
#| label: extension

```
